---
title: "MA_exposure"
author: "Yingjie"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: inline
---


# Setup 
```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(LANG = "en")

### To clear your environment
remove(list = ls())

## Load directories
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
getwd()
dir.root <- dirname(getwd())
# setwd(dir.root)

getwd()

## Load common packages
source("./code/_pkgs_dirs.R")

## Additional packages
library(googlesheets4)
library(rprojroot)
library(tidyverse)
library(stringr)
library(splitstackshape) ## `cSplit()`
library(Hmisc)
library(rworldmap)
library(ggpubr)

### packages for meta-analysis
# install.packages("remotes")
# remotes::install_github("guido-s/meta", ref = "develop")
### or an old version that supports R3.6
# url <- 'https://cran.r-project.org/src/contrib/Archive/meta/meta_4.15-0.tar.gz'
# install.packages(url, repos=NULL, type="source")
library(meta)
library(metafor)


today <- format(Sys.time(), "%Y%m%d"); today ## "%Y%m%d%H%M"
```


```{r - functions}
source('./code/func_expand_col_to_long.R')
source('./code/func_clean_indicators.R')
source('./code/func_clean_indicatorsPro.R')
source('./code/func_clean_tools.R')
source('./code/func_clean_exposure.R')
source('./code/func_clean_effectsize.R')
source('./code/func_clean_nature.R')
source('./code/func_to_sd.R')

source('./code/func_plot_freq.R')
source('./code/func_alluvial.R')
source('./code/func_ggsave.R')
```


# Data

## Load data from Covidence

```{r}

## load data 
fs <- list.files(path = "./data/0301-MA-input/", pattern = '^df_covidenceFull', full.names = T); 
# fs;

##' select the up-to-date data, which is the second to the last
f1 <- fs[(length(fs)-1)]; f1
##' select the gsheet data file
f2 <- fs[(length(fs)-0)]; f2 

df <- readRDS(file = f1) %>%
  dplyr::rename(
    'exposure_type'   = 'Nature exposure type',
    'nature_type'     = "General category of urban nature",
    'nature_quantity' = "Nature quantity measure metric",
    "n_participants"  = "Total number of participants",
    "buffers"         = "Buffer zone size considered for nature exposure measurement",
    "buffers_unit"    = "Buffer zone size's unit"  
                  ) %>%
  dplyr::mutate(effect_size_indices = `Effect size indices`) %>%
  dplyr::mutate(
    nature_quantity = gsub("Normalized Difference Vegetation Index \\(NDVI\\)", "NDVI", nature_quantity),
    # remove text within parenthesis 
    `Health outcome direction` = gsub("\\s*\\([^\\)]+\\)", "", `Health outcome direction`), 
    ) %>%
  
  func_clean_nature_type(data = ., column_name = 'nature_type') %>%
  func_clean_nature_quant(data = ., column_name = 'nature_quantity') %>%
  func_clean_bufferunit(data = ., column_name = 'buffers_unit') %>%
  func_clean_tools(data = ., column_name = 'Tools') %>%
  func_clean_exposure(data = .) %>%
  ## clean messy text in `effect_size_indices`
  func_clean_effectsize(data = .) %>%
  dplyr::mutate(
    effect_size_indices = gsub("Other: |Other:", "", effect_size_indices),
    # effect_size_indices = gsub("=.*", "", effect_size_indices), ## remove everything after "="
    effect_size_indices = trimws(effect_size_indices)
                ) %>%
  as.data.frame()
# names(df)



df2 <- readRDS(file = f2) %>%
  as.data.frame()
```


## Clean data

```{r}
## selected variables for further analysis
cols_keep <- c('Indicator', 'Tools', 'nature_type',  'nature_quantity', 'exposure_type')

df_exp <- df %>%
  dplyr::select(1:7, all_of(cols_keep)) %>%
  ## clean text in `exposure_type`
  dplyr::filter(!is.na(exposure_type)) %>%
  dplyr::mutate(exposure_type = gsub("Other: |Other:", "", exposure_type)) %>%
  dplyr::mutate(exposure_type = gsub("\\s*\\([^\\)]+\\)", "", exposure_type)) %>% # remove text within parenthesis
  as.data.frame()


## unify exposure names
f <- 'https://docs.google.com/spreadsheets/d/11oUNNjsmzC4wvYwcE8Zm_qavww0D6Twxl8UoPve1WOE/edit?usp=sharing'
exposure_tier <- googlesheets4::read_sheet(f, sheet = 'nature_exposure_channels') %>%
  dplyr::select(-exposure_type_t3) %>%
  as.data.frame()

df_exp_l <- df_exp %>% 
  ## expand `exposure_type` if there are > 1 exposure types in a study
  expand_col_to_long(data = ., target_col = 'exposure_type') %>%
  ## clean the messy text data due to manual entry 
  func_clean_exposure(data = .) %>%
  dplyr::mutate(
    # exposure_type = gsub("L4 physical activity", "L4 - physical activity in nature", exposure_type),
    # exposure_type = gsub("L1 surrounding greenness", "L1 - neighborhood/residential exposure", exposure_type),
    # exposure_type = gsub("L2 objective accessibility", "L2 - objective accessibility", exposure_type),
    # exposure_type1 = ifelse(str_detect(exposure_type, regex('duration', ignore_case = T)), 'Time spent in nature', exposure_type),
    exposure_type = ifelse(grepl(x = exposure_type, 'duration|Spending hour|Time spent', ignore.case = T), 
                           'Duration in nature', exposure_type),
    ) %>%
  left_join(., y = exposure_tier,
            by = 'exposure_type') %>%
  dplyr::rename('exposure_type_t1' = 'exposure_type') %>%
  
  ## to decide which tier name for the next step analysis
  dplyr::rename('exposure_type'    = 'exposure_type_t2') %>%
  as.data.frame()
```


### stat on exposure

```{r **To-do**}
```
  [] 'L4' needs to be further clarified 
  

```{r}

df_exp_l_stat <- df_exp_l %>% 
  group_by(exposure_type_t1, exposure_type) %>%
  dplyr::count() %>%
  ungroup() %>%
  as.data.frame()

df_exp_l_stat2 <- df_exp_l_stat %>%
  group_by(exposure_type) %>%
  dplyr::summarise_at(c('n'), sum, na.rm = T) %>%
  ungroup() %>%
  dplyr::filter(!is.na(exposure_type)) %>%
  as.data.frame()


plot_freq(data = df_exp_l_stat2, var = 'exposure_type') +
   geom_text(aes(label = n), vjust = .5, hjust = 0)

f <- paste0('stats_nat_exp_', today, '.png')
fname <- paste0(dir.fig, f); fname
func_ggsave(fname = fname, w = 7, h = 4, save_png = T)
```


### stat on exposure-tool pair

```{r}

df_exp_l_toolL <- df_exp_l %>%
  dplyr::mutate(Tool = gsub("Other: ", "", Tools),
                ##' remove text within parenthesis 
                Tool = gsub("\\s*\\([^\\)]+\\)", "", Tool)) %>%
  expand_col_to_long(data = ., target_col = "Tool") %>%
  dplyr::mutate(
    Tool = gsub(".*Likert.*|.*likert.*", "Likert scale", Tool),
    # Tool = gsub(";", "", Tool),
    ) %>% 
  func_clean_tools(data = ., column_name = 'Tool') %>%
  dplyr::select(1:Tools, Tool, everything()) %>%
  arrange(Tool)



df_exp_tool_flow <- df_exp_l_toolL %>%
  group_by(Tool, exposure_type) %>%
  tally() %>%
  as.data.frame() %>%  
  pivot_longer(names_to  = 'dimension', 
               values_to = 'layers', 
               cols = c('Tool', 'exposure_type')) %>%
  group_by(dimension) %>%
  dplyr::mutate(id_within_layers = row_number(dimension)) %>%
  arrange(dimension) %>%
  dplyr::rename(freq = n) %>%
  dplyr::mutate(
    dimension = factor(dimension, levels = c('Tool', 'exposure_type')),
    ) %>%
  group_by(layers) %>%
  dplyr::mutate(total = sum(freq, na.rm = T)) %>%
  as.data.frame()

width_my <- 1/2
sorted <- T  ## sorted by flow size
sorted <- NA ## default setting, sorted alphabetically 

indicator_n_min <- 5 ## only map indicators with more than 5 times
# Labeling small strata
labele_small <- 5


func_alluvial(data = df_exp_tool_flow, indicator_n_min = 5, width_my = width_my, w_p = 7,
              show_y_ticks = F, 
              filename.prefix = '', filename.postfix = 'tool_exposure')



### only include the top 3 MH tools ------------------------------------------------------
tool_selected <- c('GHQ-12', 'PANAS', 'POMS')
# df_exp_tool_flow3 <- df_exp_tool_flow %>%
#   dplyr::mutate(remove = ifelse(dimension == 'Tool' & !layers %in% tool_selected, 0, 1)) %>%
#   dplyr::filter(remove != 0) %>% dplyr::select(-remove)

df_exp_tool_flow3 <- df_exp_l_toolL %>%
  dplyr::filter(Tool %in% tool_selected) %>% 
  group_by(Tool, exposure_type) %>%
  tally() %>%
  as.data.frame() %>%  
  pivot_longer(names_to  = 'dimension', 
               values_to = 'layers', 
               cols = c('Tool', 'exposure_type')) %>%
  group_by(dimension) %>%
  dplyr::mutate(id_within_layers = row_number(dimension)) %>%
  arrange(dimension) %>%
  dplyr::rename(freq = n) %>%
  dplyr::mutate(
    dimension = factor(dimension, levels = c('Tool', 'exposure_type')),
    ) %>%
  group_by(layers) %>%
  dplyr::mutate(total = sum(freq, na.rm = T)) %>%
  as.data.frame()

func_alluvial(data = df_exp_tool_flow3, indicator_n_min = 5, width_my = width_my, w_p = 7,
              show_y_ticks = F, 
              filename.prefix = '', filename.postfix = 'tool3_exposure')
```


## Prepare data for MA

### subset one `exposure_type`

#### - GHQ-12
```{r}
mh_tool           <- "GHQ-12"

# exposure_type_i   <- 'L1 - neighborhood/residential exposure'
exposure_type_i   <- c('Residential')

effect_size_ind_i <- c('coefficients')
  

## test 
# df_test <- df %>%
#   dplyr::mutate(effect_size_indices = `Effect size indices`) %>%
#   func_clean_effectsize(data = .) %>%
#   dplyr::select(effect_size_indices, `Effect size indices`) %>%
#   dplyr::mutate(len = str_length(effect_size_indices)) %>%
#   arrange(desc(len)) %>%
#   as.data.frame()



###' subset papers that examined `exposure_type_i`
###' 

func_exp_subset <- function(df, exposure_type_i, mh_tool) {
  
  ## get paper id
  exp_sub <- df_exp_l %>%
    dplyr::filter(exposure_type %in% exposure_type_i)
  exp_sub_id <- unique(exp_sub$id)

  ## subset based paper id
  exp_sub_df <- df %>%
    dplyr::filter(id %in% exp_sub_id) %>%
    dplyr::filter(str_detect(Tools, mh_tool)) %>%
    
    ## subset cols -------------------------------------------------------------------------
    dplyr::select(id:`Effect size indices`, effect_size_indices, 
                  everything()) %>%
    dplyr::select(id:Country, 
                  all_of(cols_keep), 
                  n_participants, buffers, buffers_unit,
                  effect_size_indices:ncol(.)) %>%
    dplyr::select(-c(Title:meet_criteria)) %>%
    dplyr::select(-contains(c('Please specify the tables', 'Additional comments'))) %>%
    as.data.frame()
  
  return(exp_sub_df)
  
}

exp_sub_df <- func_exp_subset(df = df, exposure_type_i = exposure_type_i, mh_tool = mh_tool)
sub_ghq <- exp_sub_df

## save for later use
f <- paste0('./data/0301-MA-input/', 'sub_ghq.RData')
save(mh_tool, exposure_type_i, effect_size_ind_i, exp_sub_df, file = f)
```



#### - PANAS
```{r}
mh_tool           <- "PANAS"

# exposure_type_i   <- c('stay static in nature', 'physical activity in nature') 
exposure_type_i   <- c('In nature - static', 'In nature - PA')
 

## [] TBD - clean the data
effect_size_ind_i <- c("Mean_pre_post")
  


exp_sub_df <- func_exp_subset(df = df, exposure_type_i = exposure_type_i, mh_tool = mh_tool)
sub_panas <- exp_sub_df

## save for later use
f <- paste0('./data/0301-MA-input/', 'sub_panas.RData')
save(mh_tool, exposure_type_i, effect_size_ind_i, exp_sub_df, file = f)
```



#### - POMS
```{r}
mh_tool           <- "POMS"

# exposure_type_i   <- c('stay static in nature', 'physical activity in nature') 
exposure_type_i   <- c('In nature - static', 'In nature - PA')
 

## [] TBD - clean the data
effect_size_ind_i <- c(
  "D",
  "d",
  "Mean_pre_post")
  
###' subset papers that examined `exposure_type_i`
exp_sub_df <- func_exp_subset(df = df, exposure_type_i = exposure_type_i, mh_tool = mh_tool)
sub_poms <- exp_sub_df

## save for later use
f <- paste0('./data/0301-MA-input/', 'sub_poms.RData')
save(mh_tool, exposure_type_i, effect_size_ind_i, exp_sub_df, file = f)
```





## Choose and load input data

  Now, each paper can include data from multiple models, and they are presented in columns. 
We need to put all data on models in rows. 

```{r - choose one as input}

f <- paste0('./data/0301-MA-input/', 'sub_ghq.RData')
f <- paste0('./data/0301-MA-input/', 'sub_panas.RData')
# f <- paste0('./data/0301-MA-input/', 'sub_poms.RData')

load(file = f)
```



### format data
```{r - wide to long format}

##' Test code for formatting one model
# exp_sub_mod1 <- exp_sub_df %>%
#   dplyr::select(id, starts_with("Model 1 ") & !contains("measurement", ignore.case = TRUE))
# 
# exp_sub_mod11 <- exp_sub_df %>%
#   dplyr::select(id, starts_with("Model 11 "))


##' loop all 20 models (in the Covidence form, we have 20 rows for data extraction)
exp_sub_l <- data.frame()
for (i in 1:20) {
  # print(i)
  mod_id <- paste0("Model ", i, " ")
  exp_sub_dfi <- exp_sub_df %>%
    dplyr::select(id, 
                  all_of(cols_keep),
                  effect_size_indices, `Health outcome direction`, 
                  n_participants, buffers, buffers_unit,
                  ##' loop a model by selecting the column names 
                  ##' but need to exclude data from table 3 (with column names that contain key word 'measurement')
                  starts_with(mod_id) & !contains("measurement", ignore.case = TRUE)) %>%
    dplyr::mutate(model_id = i) %>%
    dplyr::select(id, effect_size_indices, model_id, `Health outcome direction`, everything())
  
  ##' remove model id so that they can be rbind (require the same column names)
  colnames(exp_sub_dfi) <- sub(mod_id, "", colnames(exp_sub_dfi))
  ##' Remove part of string after "."
  colnames(exp_sub_dfi) <- gsub("\\..*","",colnames(exp_sub_dfi))
  
  ##' Repair duplicate names - specify your own name repair function
  exp_sub_dfi <- exp_sub_dfi %>%
    as_tibble(., .name_repair = make.unique) %>%
    as.data.frame()
  
  exp_sub_l <- rbind(exp_sub_l, exp_sub_dfi)
}

rm(exp_sub_dfi)
```



```{r - clean names from table 1/2, include=FALSE}

## for data extracted in table option 1
exp_sub_l_o1 <- exp_sub_l %>%
  dplyr::select(id:Notes) %>%
  as.data.frame()
name1 <- names(exp_sub_l_o1) %>%
  gsub('\\.1|\\.2', '', .) %>%
  gsub('Other covariates that are beyond the baseline', 'Other_covariates_o1', .)
name1.1 <- name1[1: (which(name1 == 'MH_indicator')-1)]
name1.2 <- name1[which(name1 == 'MH_indicator'):length(name1)] %>% paste0(., '_o1')
names(exp_sub_l_o1) <- c(name1.1, name1.2) 
names(exp_sub_l_o1)



## for data extracted in table option 2
exp_sub_l_o2 <- exp_sub_l %>%
  dplyr::select(id, model_id, Notes:Notes.1) %>%
  dplyr::select(-Notes)
name2 <- names(exp_sub_l_o2) %>%
  gsub('\\.1|\\.2', '_o2', .) %>%
  gsub('Other covariates that are beyond the baseline', 'Other_covariates', .)
names(exp_sub_l_o2) <- name2  
names(exp_sub_l_o2)


## combine data from table option 1 and option 2 -----------------------------------------
exp_sub_long <- exp_sub_l_o1 %>%
  left_join(., exp_sub_l_o2, by = c("id", "model_id")) %>%
  func_clean_indicatorsPro(data = ., column_name = 'Indicator') %>%
  func_clean_indicatorsPro(data = ., column_name = 'MH_indicator_o1') %>%
  func_clean_indicatorsPro(data = ., column_name = 'MH_indicator_o2') %>%
  func_clean_buffer(data = ., column_name = 'buffer_o1') %>%
  func_clean_buffer(data = ., column_name = 'buffer_o2') %>%
  as.data.frame()

## remove these two df after merging
rm(exp_sub_l_o1, exp_sub_l_o2)
```



```{r - clean numeric values}
### clean up the negative sign "-" in data
test <- exp_sub_long %>%
  dplyr::filter(id %in% c(387)) ## take the character from this paper

m <- gsub(' ', '', test$Mean)
m <- "−0.23"
sign <- m[1] %>% substr(., 1, 1)
sign
# mm <- gsub(sign, '-', m)
# mm
# as.numeric(mm)
rm(test)
sign <- paste(sign, '−', sep = '|')


func_clean_number <- function(data, column_name){
  
  # Check if the specified column exists in the data frame
  if (!(column_name %in% colnames(data))) {
    stop("Column not found in the data frame.")
  }
  
  column_name_new <- column_name %>%
    gsub("Control_",   "c_", .) %>%
    gsub("Treatment_", "e_", .) %>%
    as.character() %>%
    str_to_lower()
    
    
  # Manipulate the specified column using multiple pipes
  d <- data %>%
    dplyr::mutate(
      !!column_name_new := !!sym(column_name),
      !!column_name_new := as.character(!!sym(column_name_new)),
      !!column_name_new := gsub(sign, "-", !!sym(column_name_new)),
      !!column_name_new := gsub(" ", "", !!sym(column_name_new)), 
      !!column_name_new := str_squish(!!sym(column_name_new)),
      !!column_name_new := trimws(!!sym(column_name_new)),
      !!column_name_new := as.numeric(!!sym(column_name_new))
    ) %>%
    dplyr::select(1:!!sym(column_name), !!column_name_new, everything()) %>%
    as.data.frame()
  return(d)
}

### test code
# exp_sub_long_clean1 <- exp_sub_long %>%
#   func_clean_number(column_name = 'Mean')

exp_sub_long_clean <- exp_sub_long %>%
  dplyr::filter(!is.na(Mean) | !is.na(Treatment_Mean) | !is.na(Treatment_Mean)) %>%
  
  ##' clean the special character "-" in text
  func_clean_number(data = ., column_name = 'Mean') %>%
  func_clean_number(data = ., column_name = 'SD') %>%
  func_clean_number(data = ., column_name = 'SE') %>%
  func_clean_number(data = ., column_name = 'CI_95_lower') %>%
  
  func_clean_number(data = ., column_name = 'Control_Mean') %>%
  func_clean_number(data = ., column_name = 'Control_SD') %>%
  func_clean_number(data = ., column_name = 'Control_SE') %>%
  func_clean_number(data = ., column_name = 'Control_CI95lower') %>%
  
  func_clean_number(data = ., column_name = 'Treatment_Mean') %>%
  func_clean_number(data = ., column_name = 'Treatment_SD') %>%
  func_clean_number(data = ., column_name = 'Treatment_SE') %>%
  func_clean_number(data = ., column_name = 'Treatment_CI95lower') %>%
  dplyr::mutate(

    ci_95_lower = ifelse(`Health outcome direction` == "Higher is better", -ci_95_lower, ci_95_lower),
    
    N = gsub(" ", "", N), 
    ## use "n_participants" to fill data gaps of N in data extraction tables
    N = ifelse(is.na(N) & !is.na(n_participants), n_participants, N),
    N = as.numeric(N),
    
    ) %>%
  
  ## clean text in nature-related columns 
  func_clean_nature_type(data = ., column_name = 'nature_type_o1') %>%
  func_clean_nature_type(data = ., column_name = 'nature_type_o2') %>%
  func_clean_nature_quant(data = ., column_name = 'nature_quantity_o1') %>%
  func_clean_nature_quant(data = ., column_name = 'nature_quantity_o2') %>%
  
  ## fill blanks using data from the column `Tools`, but only if there is only one tool in `Tools`
  func_fill_tool(data = ., column_name = "MH_tool_o1") %>%
  func_fill_tool(data = ., column_name = "MH_tool_o2") %>%
  
  dplyr::select(id, all_of(cols_keep), 
                effect_size_indices:Mean, mean, 
                CI_95_lower, ci_95_lower, everything()) %>%
  arrange(effect_size_indices, id, model_id) %>%
  as.data.frame()
```


### subset one `effect_size_indice`

```{r}

if (length(effect_size_ind_i) == 1) {
  if(effect_size_ind_i == 'coefficients') {
    exp_sub_mods <- exp_sub_long_clean %>%
      dplyr::mutate(
       mean = case_when(
          effect_size_indices == 'coefficients' & `Health outcome direction` == "Higher is better" ~ -mean,
          effect_size_indices == 'or' & `Health outcome direction` == "Higher is better" ~ 1-(mean-1),
          TRUE ~ mean
          ),
      )
  } else {
    exp_sub_mods <- exp_sub_long_clean
  } 
} else {
  exp_sub_mods <- exp_sub_long_clean
}
  


## 
unique(exp_sub_mods$effect_size_indices)

if (mh_tool == 'GHQ-12') {
  exp_sub_mods_coef <- exp_sub_mods %>%
    dplyr::filter((str_detect(pattern = paste(effect_size_ind_i, collapse = "|"), string = effect_size_indices))) %>%
    as.data.frame() 
  
  } else if (mh_tool == 'PANAS') {
    exp_sub_mods_md <- exp_sub_mods %>%
      dplyr::filter((str_detect(pattern = paste(effect_size_ind_i, collapse = "|"), string = effect_size_indices))) %>%
      dplyr::filter(MH_tool_o1 == mh_tool | MH_tool_o2 == mh_tool) %>%
      func_clean_indicator_sub(data = ., column_name = 'MH_indicator_o1') %>%
      func_clean_indicator_sub(data = ., column_name = 'MH_indicator_o2') %>%
      as.data.frame()
    ## make a copy of the data
    exp_sub_mods_panas <- exp_sub_mods_md
    
  } else if (mh_tool == 'POMS') {
    exp_sub_mods_md <- exp_sub_mods %>%
      dplyr::filter((str_detect(pattern = paste(effect_size_ind_i, collapse = "|"), string = effect_size_indices))) %>%
      dplyr::filter(MH_tool_o1 == mh_tool | MH_tool_o2 == mh_tool) %>%
      func_clean_indicator_sub(data = ., column_name = 'MH_indicator_o1') %>%
      func_clean_indicator_sub(data = ., column_name = 'MH_indicator_o2') %>%
      as.data.frame()
    ## make a copy of the data
    exp_sub_mods_poms <- exp_sub_mods_md
      
  } else {
    print('...')
  }


## how many unique papers?
length(unique(exp_sub_mods_md$id)) %>% cat('\nFor', mh_tool, '\n In total, there are', ., 'unique papers.')
nrow(exp_sub_mods_md) %>% cat('\n In total, there are', ., 'studies. \n\n')

## for PANAS -----------------------------------------
# if (mh_tool == 'PANAS') {
#   unique(exp_sub_mods_panas$effect_size_indices)
#   
#   unique(exp_sub_mods_panas$Tools) 
#   unique(exp_sub_mods_panas$MH_tool_o1)
#   unique(exp_sub_mods_panas$MH_tool_o2) 
#   
#   unique(exp_sub_mods_panas$MH_indicator_o1)
#   unique(exp_sub_mods_panas$MH_indicator_o2)
# }

```
  
# Meta-analysis

  --> Ref to `010a_MA_intro.Rmd` for more background knowledge. 

```{r functions}
# Calculate s_pooled - pooled standard deviation (SD) of both groups
sd_pooled <- function(n1, n2, sd1, sd2) {
  sd_p <- sqrt(
    ( ((n1-1)*sd1^2) + ((n2-1)*sd2^2) )/
      ((n1-1)+(n2-1))
  )
  return(sd_p)
}

# Calculate the standard error (SE)
se_pooled <- function(n1, n2, sd1, sd2) {
  se_p <- sd_pooled(n1, sd1, n2, sd2) * sqrt((1/n1)+(1/n2))
  return(se_p)
}
```
