---
title: "Untitled"
author: "Yingjie"
date: "`r Sys.Date()`"
output: html_document
---

# Setup 
```{r, include=FALSE}

```

# Meta-analysis

## Correlation

  Correlations are restricted in their range, and it can introduce bias when we estimate the standard error for studies with a small sample size (Alexander, Scozzaro, and Borodkin 1989).
  
  The (Pearson or product-moment) correlation coefficient quantifies the direction and strength of the (linear) relationship between two quantitative variables and is therefore frequently used as the outcome measure for meta-analyses. Two alternative measures are a bias-corrected version of the correlation coefficient and Fisher's r-to-z transformed correlation coefficient.



### metafor 
  * ri, the vector with the raw correlation coefficients
  * ni, the corresponding sample sizes. 

The options for the measure argument are then:
  * "COR" for the raw correlation coefficient,
  * "UCOR" for the raw correlation coefficient corrected for its slight negative bias (based on equation 2.3 in Olkin & Pratt, 1958),
  * "ZCOR" for Fisher's r-to-z transformed correlation coefficient (Fisher, 1921).

```{r}
# load the metafor package
library(metafor)

## [] need to fix data that are out of range later ... 
exp_sub_mods_cor <- exp_sub_mods_coef %>%
  dplyr::filter(!is.na(mean)) %>%
  dplyr::filter(mean <=1 & mean >=-0.6)
  

dat <- escalc(data=exp_sub_mods_cor, measure="ZCOR", ri=mean, ni=n)
study_label <- paste(dat$id, dat$model_id, sep = '_')
MH_tool_o1_list <- unique(exp_sub_mods_cor$MH_tool_o1); MH_tool_o1_list

res <- metafor::rma(yi, vi, data=dat, slab = study_label)
res
predict(res, transf=transf.ztor) ## ztor: z to r

# outlier/influence diagnostics
par(mar=c(5,6,4,2))
plot(influence(res), cex=0.8, las=1)
```


```{r - auto-report, eval=FALSE, include=FALSE}
### reporter() function
dir.report <- paste0('./figures/'); dir.report
metafor::reporter(res, dir = dir.report)

# reporter(res, format="pdf", 
#          dir = paste0(dir.root, '/figures/'), 
#          filename = 'report_metafor.PDF')
#          
# reporter(res, format="word")

### add an outlier
# dat$yi[6] <- 2.5
# res <- rma(yi, vi, data=dat)
# reporter(res)
```



### meta
```{r}
m.cor <- meta::metacor(
  data = exp_sub_mods_cor,
  cor = mean, 
  n = n,
  studlab = study_label,
  fixed = FALSE,
  random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "Health and Wellbeing")
summary(m.cor)
```


## Heterogeneity

  If the confidence interval around τ^2 does not contain zero, it indicates that some between-study heterogeneity exists in our data. 
  The value of τ is x, meaning that the true effect sizes have an estimated standard deviation of SD=x, expressed on the scale of the effect size metric.
  
  A look at the second line reveals that I^2= 63% and that H (the square root of H2) is 1.64. This means that more than half of the variation in our data is estimated to stem from true effect size differences. Using Higgins and Thompson’s “rule of thumb”, we can characterize this amount of heterogeneity as moderate to large.
  
  Here is how we could report the amount of heterogeneity we found in our example:

  ```The between-study heterogeneity variance was estimated at ^τ2 = 0.08 (95%CI: 0.03-0.35), with an I2 value of 63% (95%CI: 38-78%). The prediction interval ranged from g = -0.06 to 1.21, indicating that negative intervention effects cannot be ruled out for future studies.```


### Forest plot
  https://wviechtb.github.io/metafor/reference/forest.rma.html
```{r - forest, warning=FALSE}
### forest plot --------------------------------------------------------------------------
# forest(res)
# forest(res, addpred=TRUE, header=TRUE)
# print(forest(res, addpred=TRUE, header=TRUE))
xlim_custmize = c(-1,1)

f <- paste0('./figures/', 'forest_cor/', paste(MH_tool_o1_list, collapse = "_"), '_all_', today ,'.png'); f
png(file=f, 
    # width = 3.5, height = 4, units = 'in', 
    width = 1000, height = 1000, units = "px", pointsize = 22,
    # res = 200
    ) 
meta::forest(res, 
             addpred=TRUE, header=TRUE, 
             digits=2, 
             print.I2 = T,
             layout = "RevMan5",
             xlim=xlim_custmize, slab = study_label, shade=TRUE)
dev.off() 



# forest(res, addpred=TRUE, header=TRUE, xlim=xlim_custmize, slab = study_label) # showweights=TRUE
# forest(res, addpred=TRUE, header=TRUE, xlim=xlim_custmize, atransf=exp)
# #' optional argument to specify a function to transform the x-axis labels and annotations (e.g., atransf=exp)
# forest(res, addpred=TRUE, header=TRUE, xlim=xlim_custmize, atransf=exp, at=log(c(.6, .8, 1, 1.2, 1.4)))
```


* NOT in use
```{r - subgroup - to be fixed, eval=FALSE, include=FALSE}
# a little helper function to add Q-test, I^2, and tau^2 estimate info
mlabfun <- function(text, res) {
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=2, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(res$I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")")))}

# set up forest plot (with 2x2 table counts added; the 'rows' argument is
# used to specify in which rows the outcomes will be plotted)
# forest(res, addpred=TRUE, header=TRUE, xlim=xlim_custmize, slab = study_label)
forest(res, 
       addpred=TRUE, 
       slab = study_label,
       # xlim=c(-16, 4.6), at=log(c(0.05, 0.25, 1, 4)), 
       # atransf=exp,
       # ilab=cbind(dat$tpos, dat$tneg, dat$cpos, dat$cneg),
       # ilab.xpos=c(-9.5,-8,-6,-4.5), cex=0.90, 
       # ylim=c(-1, 27),            ## add extra space in plot
       order=dat$nature_quantity, 
       # rows=c(3:4,9:15,20:23),    ## set positions
       mlab=mlabfun("RE Model for All Studies", res),
       psize=1, header="Author(s) and Year")

# set font expansion factor (as in forest() above) and use a bold font
op <- par(cex=0.90, font=2)


# switch to bold italic font
par(font=4)

# add text for the subgroups
text(-16, c(24,16,5), pos=4, c("Systematic Allocation",
                               "Random Allocation",
                               "Alternate Allocation"))

# set par back to the original settings
par(op)

# fit random-effects model in the three subgroups
res.s <- rma(yi, vi, subset=(nature_quantity=="NDVI"), data=dat)
res.r <- rma(yi, vi, subset=(nature_quantity=="Percentage of greenspace"),     data=dat)
res.a <- rma(yi, vi, subset=(nature_quantity=="Other: Percentage of greenspace; Percentage of bluespace; presence of a garden"),  data=dat)

# add summary polygons for the three subgroups
addpoly(res.s, row=18.5, cex=0.90, 
        # atransf=exp, 
        mlab=mlabfun("RE Model for Subgroup", res.s))
addpoly(res.r, row= 7.5, cex=0.90, 
        # atransf=exp, 
        mlab=mlabfun("RE Model for Subgroup", res.r))
addpoly(res.a, row= 1.5, cex=0.90, 
        # atransf=exp, 
        mlab=mlabfun("RE Model for Subgroup", res.a))

# fit meta-regression model to test for subgroup differences
res <- rma(yi, vi, mods = ~ nature_quantity, data=dat)

# add text for the test of subgroup differences
text(x = -16, y = -1.8, pos=4, cex=0.90, bquote(paste("Test for Subgroup Differences: ",
     Q[M], " = ", .(formatC(res$QM, digits=2, format="f")), ", df = ", .(res$p - 1),
     ", p = ", .(formatC(res$QMp, digits=2, format="f")))))
```



```{r - forest - meta - plot}
width_forestPlot = 40
height_cm <- nrow(exp_sub_mods_cor)/1.1

f <- paste0('./figures/', 'forest_cor/', paste(MH_tool_o1_list, collapse = "_"), '_all_', today, '_meta.png'); f
png(filename = f, 
    # width = 3000, height = 3000, units = "px", pointsize = 22,
    width = width_forestPlot, height = height_cm/1.5, units = "cm", res = 100);
  
  
p_forest <- meta::forest(
  m.cor, 
  # sortvar = TE,
  # prediction = TRUE, 
  # print.tau2 = T,
  addpred=TRUE, 
  header=TRUE, 
  digits=2, 
  print.I2 = T,
  pooled.totals=T,
  overall = T,
  overall.hetstat = T,
  
  col.by = "black",
  col.square = "black",
  col.inside = "black",
  col.square.lines = "black",
  shade=TRUE,
  layout = "RevMan5",
  slab = study_label, shade=TRUE,
  leftlabs = c("Study ID", "g", "SE"))
p_forest

dev.off()
```


```{r - forest - meta - subgroup data}
add_subgroup_analysis <- T

subgroup_select <- 'exposure_o1'
subgroup_select <- 'nature_type_o1'

ma_cor_data <- exp_sub_mods_cor %>%
  dplyr::mutate(nature_type_o1 = str_to_sentence(nature_type_o1),
                nature_type_o1 = case_when(
                  nature_type_o1 %in% c("Other natural space/element", 'Garden', 
                                        "Green view", "Views of nature",
                                        "Greenspace - forest/tree", "Neighbourhood greenness" ,
                                        "Public natural spaces",
                                        "Greenspace use") ~ "Greenspace",
                  nature_type_o1 == "Home/ courtyard garden" ~ "Greenspace",
                  nature_type_o1 == "Community private green space" ~ "Greenspace",
                  T ~ nature_type_o1
                )) %>%
  dplyr::filter(!is.na(exposure_o1)) %>%
  dplyr::mutate(subgroup_selected = !!sym(subgroup_select)) 

unique(ma_cor_data$exposure_o1)
unique(ma_cor_data$nature_type_o1)

ma_cor <- meta::metacor(
  data = ma_cor_data,
  cor = mean, 
  n = n,
  studlab = study_label,
  fixed = FALSE,
  random = TRUE,
  method.tau = "REML",
  tau.common = TRUE,
  hakn = TRUE,
  title = "Health and Wellbeing")


h_just <- nrow(ma_cor_data)/50


## update the MA by adding subgroup analysis ---------------------------------------------
if (add_subgroup_analysis == T) {
  ma_cor <- ma_cor %>%
    # dplyr::mutate(subgroup_selected = !!sym(subgroup_select)) %>%
    # dplyr::filter(!is.na(subgroup_selected)) %>%
    update(., subgroup = subgroup_selected)
  
  test.effect.subgroup.random_para = TRUE
  postfix_subgroup <- paste0("subgroup_", subgroup_select)
  height_cm <- height_cm
    
  } else {
    test.effect.subgroup.random_para = F
    postfix_subgroup <- ""
  }



## extract the overall effect size data to a dataframe ===================================

ma_result.overall <- data.frame()
ma_result.subgroup <- data.frame()

### 1. overall model data
ma_cor.df <- data.frame(
  tool = paste(MH_tool_o1_list, collapse = ";"), 
  ind_sub = paste(MH_tool_o1_list, collapse = ";"),
  subgroup = 'Overall',
  es.mean = ma_cor$TE.random,
  es.lower= ma_cor$lower.random,
  es.upper= ma_cor$upper.random,
  pval    = ma_cor$pval.random %>% round(., digits = 10),
  I2      = as.numeric(ma_cor$I2) %>% round(., digits = 2),
  p_subgroup = NA,
  ## Number of studies
  n_study = ma_cor$k.all,
  ## Number of observations
  n_obs   = sum(ma_cor$n, na.rm = T)
) %>%
  dplyr::mutate(
    p.star  = case_when(pval < 0.001 ~ '***',
                      pval < 0.01 ~ '**',
                      pval < 0.05 ~ '*',
                      T ~ ''),
  )
ma_result.overall <- rbind(ma_result.overall, ma_cor.df)

### 2. subgroup model data
if (add_subgroup_analysis == T) {
  ma_cor.df.subgroup <- data.frame(
    tool = paste(MH_tool_o1_list, collapse = ";"), 
    ind_sub = paste(MH_tool_o1_list, collapse = ";"), 
    subgroup = names(ma_cor$TE.common.w),
    es.mean = as.numeric(ma_cor$TE.random.w),
    es.lower= as.numeric(ma_cor$lower.random.w),
    es.upper= as.numeric(ma_cor$upper.random.w),
    pval    = as.numeric(ma_cor$pval.random.w) %>% round(., digits = 10),
    I2      = as.numeric(ma_cor$I2.w) %>% round(., digits = 2),
    p_subgroup = as.numeric(ma_cor$pval.Q.b.random) %>% round(., digits = 10),
    ## Number of studies
    n_study = as.numeric(ma_cor$k.all.w),
    ## Number of observations
    n_obs   = NA
  ) %>%
    dplyr::mutate(
      p.star  = case_when(pval < 0.001 ~ '***',
                        pval < 0.01 ~ '**',
                        pval < 0.05 ~ '*',
                        T ~ ''),
    )
  ma_result.subgroup <- rbind(ma_result.subgroup, ma_cor.df.subgroup)
}


## save MA result 
cat('\n')
fname <- paste0('./data/0302-MA-output/', 
                paste('ma_result.overall_', paste(MH_tool_o1_list, collapse = "_"), '.rds', sep = '')); fname
saveRDS(ma_result.overall, file = fname)

if (add_subgroup_analysis == T) {
  fname <- paste0('./data/0302-MA-output/', 
                  paste('ma_result.subgroup', paste(MH_tool_o1_list, collapse = "_"), subgroup_select, '.rds', sep = '_')); fname
  saveRDS(ma_result.subgroup, file = fname)
}
```



### Plot effect size 

```{r - forest - subgroup plot - detail}
## forest plot ---------------------------------------------------------------------------

f <- paste0('./figures/', 'forest_cor/', paste(MH_tool_o1_list, collapse = "_"), '_', postfix_subgroup, '_',  today, '_meta.png'); f
png(filename = f, 
    # width = 3000, height = 3000, units = "px", pointsize = 22,
    width = width_forestPlot/2, height = height_cm*h_just, units = "cm", res = 100)

p_forest <- meta::forest(
  ma_cor, 
  # sortvar = TE,
  # prediction = TRUE, 
  # print.tau2 = T,
  addpred=TRUE, 
  header=TRUE, 
  digits=2, 
  print.I2 = T,
  pooled.totals=T,
  overall = T,
  overall.hetstat = T,
  
  col.by = "black",
  col.square = "black",
  col.inside = "black",
  col.square.lines = "black",
  shade=TRUE,
  layout = "RevMan5",
  slab = study_label, shade=TRUE,
  leftlabs = c("Study ID", "g", "SE"))
p_forest

dev.off()
```





```{r - forest - subgroup plot - overall}
source('./code/func_plot_ma.R')

fs <- list.files(path = "./data/0302-MA-output/", 
                 pattern = paste('^ma_result.*_', mh_tool, collapse = '|', sep = ''), 
                 full.names = T);
cat('\n This', length(fs), 'files will be included:\n')
print(fs)

ma_result_all <- data.frame()
for (f in fs) {
  d <- readRDS(file = f) 
  ma_result_all <- rbind(ma_result_all, d)
}

## pool all data together 
ma_result_all %>%
  # dplyr::filter(subgroup == 'Overall') %>%
  plot_effect_size_overall(data = ., color_var = 'subgroup', show_legend = T) +
  theme(legend.position = c(0.3, 0.15)) +
  guides(color = guide_legend(title="MH Tools"))



fname <- paste0(dir.fig, 'es_combined_', paste(MH_tool_o1_list, collapse = "_"), '_', postfix_subgroup, '_',
                today, '.png'); fname
func_ggsave(fname, w = 6, h = 5.5, save_png = T)
```




  A drapery plot plots a confidence curve for each study, as well as for the average effect. The x-axis shows the effect size metric. 
  The drapery plot is available in the R package meta

```{r}

# meta::drapery(
#   x = m.cor,
#   labels = "id",
#   type = "pval",
#   legend = FALSE)
```



### Funnel plot for publication bias

  Given our assumptions, and in the case when there is no publication bias, all studies would lie symmetrically around our pooled effect size (the vertical line in the middle), within the form of the funnel. 
  
  When *publication bias* is present, we would assume that the funnel would look asymmetrical, because only the small studies with a large effect size very published, while small studies without a significant, large effect would be missing.
  
  We can see in the plot that while some studies have statistically significant effect sizes (the gray areas), others do not (white background). 
  
  - https://cjvanlissa.github.io/Doing-Meta-Analysis-in-R/smallstudyeffects.html
  
  - https://wviechtb.github.io/metafor/reference/funnel.html
  
```{r}
### funnel plot --------------------------------------------------------------------------
# funnel(res)
# funnel(res, ylim=c(0,.08), las=1)
funnel(res, ylim=c(0,.08), las=1, digits=list(2L,2), legend=TRUE)

## trim and fill method
funnel(trimfill(res), # , side = 'left'
       las=1, ylim=c(0,.08), digits=list(2L,2), 
       # cex=1.2,
       legend=TRUE)

# res
# trimfill(res)

## contour-enhanced funnel plot
# funnel(dat$yi, dat$vi, yaxis="seinv", ## "seinv" for the inverse of the standard errors
#        # xlim=c(-.5, .5),
#        # ylim=c(10, 200), 
#        xaxs="i", yaxs="i", las=1, 
#        level=c(.10, .05, .01), 
#        shade=c("white", "gray55", "gray85"), ## pink -- not significant 
#        legend=TRUE, 
#        # back="grey90",
#        hlines=NULL, ylab="Precision (1/se)")

f <- paste0('./figures/', 'funnel_cor_', paste(MH_tool_o1_list, collapse = "_"), '_', today ,'.png'); f
png(file=f, 
    width = 1000, height = 1000, units = "px", pointsize = 22) 
funnel(
  # trimfill(res, side = 'right'),
  res,
  las=1, ylim=c(0,.08), digits=list(2L,2),
  level=c(.10, .05, .01),
  shade=c("white", "gray50", "gray65"), ## pink -- not significant
  legend=TRUE,
  back="grey90",
  hlines=NULL)
dev.off() 

```








